\chapter{Acknowledgements}

To acknowledge the contribution of everyone who has helped me complete this thesis in the last three and a half years would, no doubt, contribute significantly to the page count of this thesis.
To keep this reasonably concise, I would like to first acknowledge all of the help I've received from the people who do not have a specific mention in this section.
All of the friends and work colleagues who have encouraged and spurred me on over the last few years: your contribution is not forgotten and is certainly appreciated.

I would like to thank my supervisor, Chris Evans, for providing excellent support from the outset and keeping me focused on the important tasks in hand, as well as his meticulous quality control, which have improved this thesis greatly.
Throughout the course of this thesis, I have had some fantastic opportunities to go observing and attend productive conferences, which is all thanks to Chris' drive and enthusiasm.
Chris has been a great supervisor and friend, always using his skills and knowledge to keep me optimistic and striving for the next result.

I would also like to thank all of my collaborators, in particular Ben Davies and Rolf-Peter Kudritzki, for their help and hard work, particularly at some strange times of the day (night, depending upon your time-zone).
In addition, I would like to thank my fellow students who have provided support on a huge range of different topics, which has saved me countless time and effort.

On a personal level, I would like to thank Melanie Woodward, who has not only, made this journey of a PhD with me, but also made it so much more enjoyable. Mel has helped me celebrate the highs and helped me get back on the horse during the lows.
However, Mel has not only contributed to this thesis on a personal level.
The quality of writing in this thesis (I'm not ashamed to say) is high.
I'm not ashamed to say that because it is down to the fact that Mel is an excellent editor and has spent hours studying and commenting on this thesis, improving the style, readability and flow greatly.


I would like to thank my fellow students for supporting me on a personal level.
The ``Golden Age'' of U4, which I was lucky enough to be a part of, along with Fergus Cullen and Sandy Rogers, will live long in my memory.
